Supporting Information

### 2018-04-04 SupportingInformation.Rmd
changing extinction risk figures

### LC model :
```{r fig_risk_r0_numlocs5, echo=F, cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="LC model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0_numlocs5}", fig.height=3.5, fig.width=8}
source("mydispersal.R")
set.seed(seed)
varying_d(numsims=10000,numsteps =25,numlocs=5,r=0,K=50,disp_everywhere=F)
```

```{r fig_risk_r0_numlocs25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="LC model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0_numlocs25}", fig.height=3.5, fig.width=8}
set.seed(seed)
varying_d(numsims=10000,numsteps =25,numlocs=25,r=0,K=50,disp_everywhere=F)
```

@@

```{r fig_risk_r0.05, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05}", fig.height=3.5, fig.width=8}
source("mydispersal.R")
set.seed(seed)
r<-0.05
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.05_K200, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05_K200}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-5
K<-200
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.05_numlocs25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05_numlocs25}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-25
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.25}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.25
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.5, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.5}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.5
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.6, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.6}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.6
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.7, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.7}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.7
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.75, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.75}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.75
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r0.9, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.9}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.9
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r1.0, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.0}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.0
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r1.25, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.25}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.25
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r1.5, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.5}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.5
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r1.75, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.75}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.75
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

```{r fig_risk_r1.95, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.95}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.95
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=F)
```

@@

```{r fig_risk_r0.05_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.05_disp_everywhere}", fig.height=3.5, fig.width=8}
source("mydispersal.R")
set.seed(seed)
r<-0.05
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.05_K200_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal); With increasing K from 50 to 200, extinction risk decreases.\\label{fig_risk_r0.05_K200_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-5
K<-200
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.05_numlocs25_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal); With increasing numlocs from 5 to 25, extinction risk decreases.\\label{fig_risk_r0.05_numlocs25_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.05
numlocs<-25
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.25_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.25_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.25
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.5_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.5_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.5
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.6_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.6_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.6
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.7_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.7_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.7
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.75_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.75_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.75
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r0.9_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r0.9_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-0.9
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r1.0_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.0_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.0
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r1.25_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.25_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.25
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r1.5_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.5_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.5
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r1.75_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.75_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.75
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

```{r fig_risk_r1.95_disp_everywhere, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R")), fig.cap="Ricker model_disp_everywhere : Plot Extinction risk vs. d(degree of dispersal).\\label{fig_risk_r1.95_disp_everywhere}", fig.height=3.5, fig.width=8}
set.seed(seed)
r<-1.95
numlocs<-5
K<-50
varying_d(numsims=10000,numsteps =25,numlocs=numlocs,r=r,K=K,disp_everywhere=T)
```

>>>>

@@

```{r fig_ext_risk, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}

source("mydispersal.R")
set.seed(seed)

rlist<-c(0,0.05,0.25,0.5,0.7,0.75,0.9,1.0,1.25,1.5,1.75,1.95)

# plot for local dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_local_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=F,ploton=F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for global dispersal in D matrix ; r=0 for LC model, r!=0 for Ricker model
pdf("./Results/ext_risk_global_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
  cat("r=",r,"\n")
  s<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
  plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d_seq,s$risk_right,type="b",col="blue")
  legend(x=-0.06,y=1.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
  mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot to show the effect of increasing numlocs for r=0 (LC model), r=0.25 (Ricker model)
pdf("./Results/ext_risk_numlocs_effect.pdf",heigh=6,width=6)
op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)
for(r in c(0,0.25)){
  cat("r=",r,"\n")
  s5<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=r,K=50,disp_everywhere=T,ploton=F)
  s25<-varying_d(numsims=10000,numsteps =25,numlocs=25,r=r,K=50,disp_everywhere=T,ploton=F)

  plot(s5$d_seq,s5$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
  lines(s25$d_seq,s25$risk_left,type="b",col="orange")
  legend("topleft", title=paste0("r=",r," , left tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('red', 'orange'),  horiz=F, bty='n')

  plot(s5$d_seq,s5$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",
       panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
  lines(s25$d_seq,s25$risk_right,type="b",col="skyblue")
  legend("topleft",title=paste0("r=",r," , right tail dep. in noise"), c("numlocs=5","numlocs=25"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')
  #mtext(paste0("B",1))
}
par(op)
dev.off()

# plot to see the effect of K for r=0.25 (Ricker model)
pdf("./Results/ext_risk_K_effect.pdf",heigh=6,width=6)
op<-par(mfrow=c(2,2),mar=c(4,4,1,1) + 0.1)

s1<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=50,disp_everywhere=F,ploton=F)
s2<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=200,disp_everywhere=F,ploton=F)

s3<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=50,disp_everywhere=T,ploton=F)
s4<-varying_d(numsims=10000,numsteps =25,numlocs=5,r=0.25,K=200,disp_everywhere=T,ploton=F)

plot(s1$d_seq,s1$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
lines(s2$d_seq,s2$risk_left,type="b",col="orange")
legend("topleft",title=("Noise : left tail dep., local disp."), c("K=50","K=200"), fill=c('red', 'orange'),  horiz=F, bty='n')

plot(s1$d_seq,s1$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
lines(s2$d_seq,s2$risk_right,type="b",col="skyblue")
legend("topleft",title=("Noise : right tail dep., local disp."),c("K=50","K=200"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')

plot(s3$d_seq,s3$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
lines(s4$d_seq,s4$risk_left,type="b",col="orange")
legend("topleft",title= ("Noise : left tail dep., global disp."),c("K=50","K=200"), fill=c('red', 'orange'),  horiz=F, bty='n')

plot(s3$d_seq,s3$risk_right,xlim=c(0,1),ylim=c(0,1),type="b",col="blue",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5)
lines(s4$d_seq,s4$risk_right,type="b",col="skyblue")
legend("topleft",title=("Noise : right tail dep., global disp."),c("K=50","K=200"), fill=c('blue', 'skyblue'),  horiz=F, bty='n')

par(op)
dev.off()
```

@@
